---
title: "CP-2-Lecture"
format: revealjs
editor: visual
---

# CP-2 Lecture

# HAVILAND - HOUR 1

# Variable Assignment

Explain that while = and can be used interchangeably in most places, it is best to just use 

R uses the =, \<-, and -\> to assign objects to variable names. The assignment will always occur when using '\<-' like in 'x \<- 3' in any context '=' may appear in function calls wherein assignment will not occur but rather values will be assigned for the functional use. Anyway.

# Vectors

The simplest, most fundamental data structure in the language. They can be composed of various data types,

A list of atomic data types in R:

-   Numeric Integer

-   Numeric Double

-   Character

-   Logical

-   *Also Complex and Raw*

# Vector Init

Example vector initiations:

```{r}
?c # combine/ concatenate
aVector <- c(1,2,3,4,5)
bVector <- 10:50
cVector <- seq(2,3,by = 0.5)
dVector <- rep(1:2, time = 3)
eVector <- rep(1:2, each = 3)


flatVect <- c(1,3,c(1,4,c(98),5))
```

# Vector functions 

apply vector functions to the above vectors, maybe sort and reverse nested

```{r}

sortVector <- sort(aVector)
revVector <- rev(aVector)
counts <- table(aVector) # factors and table go together
uniqueValues <- unique(aVector)

### Append() also

```

# Vector element selection

-   \[x\]

-   \[-x\]

-   \[x:y\]

-   \[-(x:y)\]

-   \[c(x,y)\]

-   \[X %in% c(w,y,z)\] *returns elements w,y,z*

# Built-in Math Functions

apply math functions to the vectors from above, math functions including.

max/min mean sum var/sd cor(x,y), among other math functions, which can be called on an entire vector.

# Vector Math

Vector multiplication intricacy.

# Logical Operators in R

! & && (\|) and (\|\|) difference between element wise and general???

\[x == 5\] \[x \< 5\]

# if/else/ifelse and your first function

```{r}
?ifelse
# ifelse(test, yes, no)

if{}()

if(){
  
} elseif {
  
} else {
  
}
```

```{r}
yourFunction <- function(int) {}

```
